Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-06-24 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
adjust folders

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}

# get the data file for hddm analysis
df.L.hddm <- subset(df.L, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
df.T.hddm <- subset(df.T, ACC ==1 | ACC == 0)

df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
colnames(df.L.hddm_m) <- c("subj_idx","Morality",'id','rt','response')     # change column name

df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.L.hddm_nm) <- c("subj_idx","Morality",'id','rt','response')

df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_val) <- c("subj_idx","Morality",'id','rt','response')
df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_id) <- c("subj_idx","Morality",'id','rt','response')

@@

# get all the participants who were excluded:
excldSub1 <- c(excldSub1_L, excldSub1_T)
excldSub1 <- excldSub1[!duplicated(excldSub1)]

@@

```{r preproc_match,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.L1.V.acc  <-  ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

# calculate the number of each for each condition
df.L1.V.SDT <-  ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
                     N = length(sdt))

@@

@@

```{r preproc_categ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.T1.V.acc  <-  ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

@@

## saving data ####
# merge the dprime and RT data and save
df.T1.V.sum_w <- merge(df.T1.V.acc_w,  df.T1.V.RT.subj_w,by = "Subject")

# merge the RT and ACC data (long-format)
df.T1.V.sum_rt_acc_l <- merge(df.T1.V.acc,df.T1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[order(df.T1.V.sum_rt_acc_l$Subject),]

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
setwd(curDir)

```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
df.L1.V.sum_rt_acc_l_p$cond <- paste(df.L1.V.sum_rt_acc_l_p$Morality,df.L1.V.sum_rt_acc_l_p$Identity,sep = '_')
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l_p,Morality == 'Good')
ggplot(data=df.L1.V.sum_rt_acc_l_p, aes(x=cond, y=RT, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

# plot the d prime for good other and good self
# concatenate the conditions
df.L1.V.SDT_l$cond <- paste(df.L1.V.SDT_l$Morality,df.L1.V.SDT_l$Identity, sep = '_')
# select only the moral positive coniditions
df.L1.V.SDT_l_p <- df.L1.V.SDT_l[df.L1.V.SDT_l$Morality == 'Good',]
# plot 
ggplot(data=df.L1.V.SDT_l_p, aes(x=cond, y=dprime, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

#ggstatsplot::ggbetweenstats(
#  data = df.L1.V.sum_rt_acc_l_p,
#  x = c(Morality,Identity),
#  y = RT,
#  notch = TRUE,                                   # show notched box plot
#  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
#  #type = "parametric",                            # which type of test is to be run
#  outlier.tagging = FALSE,                         # whether outliers need to be tagged
#  #outlier.label = RT,                    # variable to be used for the outlier tag
#  xlab = "conditions",                       # label for the x-axis variable
#  ylab = "Reaction time (ms)",               # label for the y-axis variable
#  title = "Dataset: Iris flower data set",        # title text for the plot
#  caption = expression(                           # caption text for the plot 
#    paste(italic("Note"), ": this is a demo")
#  ),
#  messages = FALSE
#) +                                               # further modification outside of ggstatsplot
#  ggplot2::coord_cartesian(ylim = c(500, 800)) + 
#  ggplot2::scale_y_continuous(breaks = seq(500, 800, by = 50)) 
```

>>>>

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# get the data file for hddm analysis
df.L.hddm <- subset(df.L, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
df.T.hddm <- subset(df.T, ACC ==1 | ACC == 0)

df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name

df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')

df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')

df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')

@@

# get all the participants who were excluded:
extraExcld <- c(7338)  # this participant didn't understand the instruction, one condition's Accuracy is 0
excldSub1 <- c(excldSub1_L, excldSub1_T,extraExcld)
excldSub1 <- excldSub1[!duplicated(excldSub1)]

@@

```{r preproc_match,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.L1.V.acc  <-  plyr::ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

# calculate the number of each for each condition
df.L1.V.SDT <-  plyr::ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
                     N = length(sdt))

@@

# calculate the effect of self-ref and valence
df.L1.v.sum_eff_w <- df.L1.V.sum_w[,1:3]
df.L1.v.sum_eff_w$d_Good_Self_Other <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Good_Other
df.L1.v.sum_eff_w$d_Self_Good_Bad   <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Bad_Self

df.L1.v.sum_eff_w$RT_Good_Self_Other <- df.L1.V.sum_w$RT_match_Good_Other -  df.L1.V.sum_w$RT_match_Good_Self
df.L1.v.sum_eff_w$RT_Self_Good_Bad   <- df.L1.V.sum_w$RT_match_Bad_Self -  df.L1.V.sum_w$RT_match_Good_Self

@@

```{r preproc_categ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.T1.V.acc  <-  plyr::ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

# combing data from diff task for analyzing the interaction btw val and id
df.T1.V.acc_noTask  <-  plyr::ddply(df.T1.V,.(Subject, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

df.T1.V.acc_noTask_w <- dcast(df.T1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")

# rename the column number
colnames(df.T1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.T1.V.acc_noTask_w[,2:5]), sep = "_")

@@

# combining data form different task for analyszing interaction of val and id
df.T1.V.RT.subj_noTask <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
df.T1.V.RT.subj_noTask_w <- dcast(df.T1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.T1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.T1.V.RT.subj_noTask_w[,2:5]), sep = "_")

## saving data ####
# merge the accuracy and RT data and save
df.T1.V.sum_w <- merge(df.T1.V.acc_w,  df.T1.V.RT.subj_w,by = "Subject")
df.T1.V.sum_noTask_w <- merge(df.T1.V.acc_noTask_w,  df.T1.V.RT.subj_noTask_w,by = "Subject")

## calculated effects ####
# self-reference effect
df.T1.V.sum_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
df.T1.V.sum_w$RT_Val_Bad_selfEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Bad_Self
df.T1.V.sum_w$RT_Id_Good_selfEffect  <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
df.T1.V.sum_w$RT_Id_Bad_selfEffect   <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Self
# valence effect
df.T1.V.sum_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
df.T1.V.sum_w$RT_Val_Other_valEffect <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Good_Other
df.T1.V.sum_w$RT_Id_Self_valEffect   <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self
df.T1.V.sum_w$RT_Id_Other_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Good_Other
# task effect
df.T1.V.sum_w$RT_Good_Self_taskEffect  <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Self
df.T1.V.sum_w$RT_Bad_Self_taskEffect   <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Id_Bad_Self
df.T1.V.sum_w$RT_Good_Other_taskEffect <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Other
df.T1.V.sum_w$RT_Bad_Other_taskEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Other

# calculate the effect of self-ref and valence
df.T1.v.sum_eff_w <- data.frame(df.T1.V.sum_w[,c('Subject')])
colnames(df.T1.v.sum_eff_w) <- 'Subject'
df.T1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
df.T1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
df.T1.v.sum_eff_w$RT_Id_Good_selfEffect <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
df.T1.v.sum_eff_w$RT_Id_Self_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self

df.T1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.T1.V.sum_w$ACC_Val_Good_Other - df.T1.V.sum_w$ACC_Val_Good_Self
df.T1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.T1.V.sum_w$ACC_Val_Bad_Self - df.T1.V.sum_w$ACC_Val_Good_Self
df.T1.v.sum_eff_w$ACC_Id_Good_selfEffect <- df.T1.V.sum_w$ACC_Id_Good_Other - df.T1.V.sum_w$ACC_Id_Good_Self
df.T1.v.sum_eff_w$ACC_Id_Self_valEffect  <- df.T1.V.sum_w$ACC_Id_Bad_Self - df.T1.V.sum_w$ACC_Id_Good_Self

# merge the effect file
df.v.sum_eff_all_w <- merge(df.L1.v.sum_eff_w,df.T1.v.sum_eff_w,by="Subject")

# merge the RT and ACC data (long-format) ####
df.T1.V.sum_rt_acc_l <- merge(df.T1.V.acc,df.T1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[order(df.T1.V.sum_rt_acc_l$Subject),]

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.T1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'exp7_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Good")
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

RTdata2 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Bad")
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
Ddata1 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Good")
Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = Ddata1, x = Identity, y = dprime,  
                     xlab = "Good", ylab = "d prime",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

Ddata2 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Bad")
Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = Ddata2, x = Identity, y = dprime,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
p_dprime_match <- multiplot(p1,p2,cols = 2)
# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
setwd(traDir)
tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_dprime_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
                     xlab = "Good", ylab = "Accuracy",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
                     xlab = "Good", ylab = "Accuracy",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
                     theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
                    #+ coord_cartesian(ylim=c(300,900))

#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE)+
      scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
      theme_classic() +
      theme(legend.position = "none",text=element_text(family='Times'),
                               axis.line.x=element_line(size=1.2),
                               axis.title.x =element_text(size=16),
                               axis.text.x=element_text(size=14,color = "black"),
                               axis.ticks.x=element_line(size=1.2))

setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```
